### 2020-01-01 method/sec_4-db_struct.tex
Work load precipitation and water level

\subsection{Timeseries Key Attributes}
- Module ID
  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
- Value Type
  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
- Location
  Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  - Regualr Grid locations - Contains a name which is human readable. The grid presents by deviding into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the firt cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
\end{lstlisting}
  - Irregualr Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)

>>>>

\subsection{Timeseries Key Attributes}
- Module ID
  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
- Value Type
  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
- Location
  Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
\end{lstlisting}
  - Irregular Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)

### 2020-01-01 results/sec_1-test_plan.tex
Work load precipitation and water level

@@

Following are the test cases which are planned to perform;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 5min intervals and create metadata of the timeseries
    \item Import Timeseries
    \begin{itemize}
        \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70%(max 210 requests), Vector (Multi-Scalar) - 20% (max 60 requests), Grid - 10% (max 30 requests)
    \end{itemize}
    \item Extensions
    \begin{itemize}
        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
        \item 30min of test run. Just for 5min data. (total 0.5 hours)
        \item Do with Import Timeseries with error data which will go through extensions.
    \end{itemize}
    \item Export Timeseries
    \begin{itemize}
        \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70%, Vector (Multi-Scalar) - 20%, Grid - 10% (Use the Imported - Data before and verify against Extensions)
    \end{itemize}
    \item Import + Extension + Export + Timeseries Queries (All)
    \begin{itemize}
        \item 30min test run. Change with request size from 1hr, 30min and 5min. (total 1.5 hours)
    \end{itemize}
\end{enumerate}

Throughput
Latency
Resource Utilization
Auto Scaling

>>>>

The percentage of each data type can be vary depend on the situation. But most of the applications collect many data from the weather stations in order to correct and validate the models data. These weather stations can send the data in different frequencies with different parameters such as precipitation, temperature, humidity, wind direction etc.
Most of these are scalar data. Parameters such as wind direct are vector data which has less percentage compared to scalar data. On other side, most of the grid data generate from models and simulations. Those produce in less frequency due to cost of the computer resource to produce results. After considering those factor, it is logical to come with following percentages;
\begin{itemize}
    \item Scalar - 70\%
    \item Vector - 20\%
    \item Grid - 10\%
\end{itemize}

@@

Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 5min intervals and create metadata of the timeseries
    \item Import Timeseries
    \begin{itemize}
        \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70\%(max 210 requests), Vector (Multi-Scalar) - 20\% (max 60 requests), Grid - 10\% (max 30 requests)
    \end{itemize}
    \item Extensions
    \begin{itemize}
        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
        \item 30min of test run. Just for 5min data. (total 0.5 hours)
        \item Do with Import Timeseries with error data which will go through extensions.
    \end{itemize}
    \item Export Timeseries
    \begin{itemize}
        \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
    \end{itemize}
    \item Import + Extension + Export + Timeseries Queries (All)
    \begin{itemize}
        \item 30min test run. Change with request size from 1hr, 30min and 5min. (total 1.5 hours)
    \end{itemize}
\end{enumerate}

While performance analysis following metrics are use to measure the performance of the system.
\begin{itemize}
    \item Throughput
    \item Latency
    \item Resource Utilization
    \item Auto Scaling
\end{itemize}

### 2020-01-01 results/sec_2-work_load.tex
Work load precipitation and water level

\section{Work Load Creation}

Precipitation
\begin{lstlisting}[language=sh, caption=Test Plan Help]
-h | --help: Usage
    <ROOT_DIR> <COMMAND> <REQ_SIZE>
    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
  NOTE: Modify test.conf as necessary
  e.g.
  test_plan.sh ~/wdias/wdias-performance-test run
  test_plan.sh ~/wdias/wdias-performance-test run 2
  - Run all the steps in order of setup, import, 
    create_extension, extension, export, all, query

@@

Water level

>>>>

\section{Work Load Creation}
do I need to talk about system setup with EKS?
add another section for performance tuning?

== Starts with how locations are created
As explained in the \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.

These locations https://developers.google.com/public-data/docs/canonical/countries\_csv are static though out the testing, and data added to the wdias-performance-test.
During the performance test, it creates 1000 timeseries and keep adding data against those timeseries. For each location, it creates four timeseries with vary with module Id key attribute with four values. Thus combining all together, those creates 1000 timeseries. But test cases generate these values before starts the performance tests, and able to increase the timeseries as wanted.

For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed. Since grid locations have different metadata structure as described in \ref{se:db_struct}, those data handle separately. But the locationId of grid and scalar data types have the same effect when define a timeseries.

> Then using those, create timeseries metadata (how it assure 10% of Grid data)
In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \say{randomised} - create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. - https://jmeter.apache.org/usermanual/best-practices.html\#lean_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This is occurred in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

== Then how precipitation data for each time period created
The system is capable of storing any numeric value up to 3 decimal points. It does not make any different based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing, \acrshort{jmeter} is using real precipitation data from \acrshort{curw}. One month period of data for five weather stations have been using for prepare the test data. The script to cleanup and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.

\begin{lstlisting}[language=sh, caption=Precipitation Data Preparation]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted dirs
\end{lstlisting}
When preparing the data, it create three set of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
This will reduce the overhead in performance testing and increase the performance itself.
Extract function use while creating the containers, and extract the data into the container. This reduce the context loading while creating the container images.
While performing the load testing, \acrshort{jmeter} keep update a date counter, and create over the one month data. At the end of current month, the date counter advance to the next month. But data is repeat using from the beginning. In order to provide more randomness, it switch over five locations as well. The JSR223 scripts were written in a generic way such that is possible to tweak and use if there are more location data available.

> Then how water level data for Grid time series created
Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data. One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netcdf}, and it is another domain with an attraction up to some extend.

\begin{lstlisting}[language=sh, caption=Water level Data Preparation]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file dirs based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted dirs
\end{lstlisting}
The water level also contains the real data for one month of period, and \emph{setup\_waterlevel.sh} script provide the functionality of prepare, cleanup and extract.
Also it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keep increasing.

> Talk about the test test up - JMeter
 -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
> Talk about Stepping timer with concurrent thread group
> Add screenshot of jmeter setup
> Add prod req graph
> talk about how test cases are enabled
> talk about test plans can run
\begin{lstlisting}[language=sh, caption=Test Plan Help]
-h | --help: Usage
    <ROOT_DIR> <COMMAND> <REQ_SIZE>
    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
  NOTE: Modify test.conf as necessary
  e.g.
  test_plan.sh ~/wdias/wdias-performance-test run
  test_plan.sh ~/wdias/wdias-performance-test run 2
  - Run all the steps in order of setup, import, 
    create_extension, extension, export, all, query

@@

> JMeter performance tuning
  Use CSV files rather Random generates
  Use JSR223 scripts with Grrovy
  Using Stepping Timer
